Experimenting with n-grams in Civil Procedure Codes

### 2014-08-07 experiment.Rmd
Works with new codes

```{r}
files <- dir("txt", "*.txt")
raw <- file.path("txt", files) %>%
  lapply(., scan, "character", sep = "\n")
names(raw) <- files
codes_texts <- lapply(raw, paste, collapse = " ") %>%
  lapply(., tolower) %>%
  lapply(., WordTokenizer) %>%
  lapply(., paste, collapse = " ")
```

@@

So far we have been comparing each code to the universe of codes, not one to another.
How many unique n-grams are there in total, and how many in each code?

@@

```{r}
ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt) 
ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850part2.txt))

@@

```{r}
ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt) 
ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850part2.txt))

@@

```{r}
cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
                                           codes_grams$NC1868.txt)
str(cf_ny_nc)
```

@@

```{r}
comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
                          codes_texts$NY1850part2.txt,
                          codes_texts$NC1868.txt,
                          disp_chars = 300) %>%
                            do.call(rbind.data.frame, .)
comparison_of_matches
write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
```

@@

@@

```{r, fig.height = 3, fig.width = 8}
cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
                                           codes_grams$MI1853.txt)
mi_matches <- codes_grams$MI1853.txt %in% cf_ny_mi$matches  
mi_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in MI 1853 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```

>>>>

```{r}
codes_dir <- "text"
files <- dir(codes_dir, "*.txt")
raw <- file.path(codes_dir, files) %>%
  lapply(., scan, "character", sep = "\n")
names(raw) <- files
codes_texts <- lapply(raw, paste, collapse = " ") %>%
  lapply(., tolower) %>%
  lapply(., WordTokenizer) %>%
  lapply(., paste, collapse = " ")
```

@@

How many unique n-grams are there in total, and how many in each code?

@@

```{r}
ny_to_nc_matches <- intersect(codes_grams$NC1868.txt, codes_grams$NY1850c.txt) 
ny_to_nc_possible <- unique(c(codes_grams$NC1868.txt, codes_grams$NY1850c.txt))

@@

```{r}
ny_to_mi_matches <- intersect(codes_grams$MI1853.txt, codes_grams$NY1850c.txt) 
ny_to_mi_possible <- unique(c(codes_grams$MI1853.txt, codes_grams$NY1850c.txt))

@@

```{r}
cf_ny_nc <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
                                           codes_grams$NC1868.txt)
str(cf_ny_nc)
```

@@

```{r}
comparison_of_matches <- sample_matches %>% lapply(., kwic_ngram_match,
                          codes_texts$NY1850c.txt,
                          codes_texts$NC1868.txt,
                          disp_chars = 300) %>%
                            do.call(rbind.data.frame, .)
comparison_of_matches
write.csv(comparison_of_matches, file = "out/matches_ny_nc_kwic.csv")
```

@@

Let's try this with the California 1851 code.

```{r}
cf_ny_ca <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
                                           codes_grams$CA1851.txt)
str(cf_ny_ca)
```

And the plot comparing California and New York:

```{r, fig.height = 3, fig.width = 8}
density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
ca_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
ca_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in CA 1851 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```
```

@@

```{r, fig.height = 3, fig.width = 8}
cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850c.txt,
                                           codes_grams$MI1853.txt)
mi_matches <- codes_grams$MI1853.txt %in% cf_ny_mi$matches  
mi_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in MI 1853 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```
